{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
I guess I am done rewording this overview section.

The first task was to test how easy it was for a user to search for, download, and install Tor Browser correctly for use. Since no software is useful if the user is not able to access it, we included this in the list of tasks.
Additionally, we provided three tasks which highlights Tor's ``irregular'' behavior comparatively to other
web browsers, to gauge if users were confused at the non-Google search engine, slow loading
times for videos, and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

>>>>

Tasks 1-3 test how easy it was for a user to search for, download, and install Tor Browser 
correctly for use and if they understood that they had done the tasks correctly. 
Since no software is useful if the user is not able to access it, we found it valuable
to test the usability of this process.  Additionally, tasks 4-6 highlights Tor's ``irregular'' behavior 
comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.
